Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-04-22 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
changes to appendices
more on appendix

For dCS gravity, we follow Ref.~\cite{Wagle:2021tam} which numerically calculated the QNMs of slowly-rotating BHs in this theory
and found that the axial gravitational modes have their damping time increased as we
increase the Chern-Simons coupling $\ell_{\rm dCS}$ at fixed spin $\chi$ of the BH.
%
Hence, according to the prescription of Sec.~\ref{sec:theory_specific_qnm},
this is the branch of QNMs we chose to work with.

We can now proceed to determine $\delta\omega^{(j)}$ and $\delta\tau^{(j)}$ as follows.
%
Using the fitting formula Eq.~(54a) of~\cite{Wagle:2021tam}, namely,
%
\begin{equation}
    M {\rm Re}(\omega)_{\rm dCS} = c_{1} + c_{2} \kappa \zeta + (c_{3} + c_{4} \kappa \zeta) \, (1 - \chi)^{c_{5} + c_{6} \kappa \zeta},
    \label{eq:omega_dsc_eg}
\end{equation}
%
and similarly for the imaginary part, ${\rm Im}(\sigma)_{\rm dCS} =  - 1 / \tau_{\rm dCS}$.
%
Here $\kappa = 1/(16 \pi)$, $\zeta = \ell_{\rm dCS}^{4} / (M^4 \kappa)$, and thus
%
\begin{equation}
    \kappa \zeta = (\ell_{\rm dCS} / M)^4 = \gamma_{\rm dCS},
\end{equation}
%
and $c_{i}$ (with $i=1, \dots, 6$) are fitting coefficients which can be found in
Ref.~\cite{Wagle:2021tam},~Table II.

@@

The QNMs of slowly-rotating BHs in both cubic and quartic EFT of GR where calculated in Ref.~\cite{Cano:2021myl}.
%
For the cubic EFT, we use their Eq.~(67), particularizing to $\lame = \lamo = 1$. We further linearize that equation in
$\chi$ and particularize $m=2$.
%
This process, shows that the mode labelled ``-'' is the least damped and it is the one we use.

>>>>

For dCS gravity, we follow Ref.~\cite{Wagle:2021tam} which numerically calculated the QNMs, $\sigma_{\rm dCS}$,
of slowly-rotating BHs in this theory and found that the axial gravitational modes have their damping time increased as we
increase the Chern-Simons coupling $\ell_{\rm dCS}$ at fixed spin $\chi$ of the BH.
%
Hence, according to the prescription of Sec.~\ref{sec:theory_specific_qnm},
this is the branch of QNMs we chose to work with.

We then proceed to determine $\delta\omega^{(j)}$ and $\delta\tau^{(j)}$ as follows.
%
Using the fitting formula Eq.~(54a) of~\cite{Wagle:2021tam}, namely,
%
\begin{equation}
    M \, {\rm Re}(\sigma)_{\rm dCS} = c_{1} + c_{2} \kappa \zeta + (c_{3} + c_{4} \kappa \zeta) \, (1 - \chi)^{c_{5} + c_{6} \kappa \zeta},
    \label{eq:omega_dsc_eg}
\end{equation}
%
and similarly for the imaginary part, ${\rm Im}(\sigma)_{\rm dCS} =  - 1 / \tau_{\rm dCS}$.
%
Here $\kappa = 1/(16 \pi)$, $\zeta = \ell_{\rm dCS}^{4} / (M^4 \kappa)$, and thus
%
\begin{equation}
    \kappa \zeta = (\ell_{\rm dCS} / M)^4 = \gamma_{\rm dCS},
\end{equation}
%
and $c_{i}$ (with $i=1, \dots, 6$) are fitting coefficients which can be found in
Ref.~\cite{Wagle:2021tam},~Table II.

@@

The QNMs of slowly-rotating BHs in both cubic and quartic EFT of GR where calculated in Ref.~\cite{Cano:2021myl}.
%
For the cubic EFT, we use their Eq.~(67), particularizing to $\lame = \lamo = 1$.
%
We further linearize that equation in $\chi$ and particularize $m=2$.
%
This process, shows that the mode labelled ``-'' is the least damped and it is the one we use.
%
Direct comparison with Eqs.~\eqref{eq:qnm_nongr_iso} results in,
%
\begin{align}
    p_{\rm cEFT} = 4, \quad \delta \omega_{\rm cEFT}^{(0)} = - 0.5813, \quad \delta \tau_{\rm cEFT}^{(0)} = 2.6469,
    \nonumber \\
    \delta \omega_{\rm cEFT}^{(1)} = -3.8620, \quad \delta \tau_{\rm cEFT}^{(1)} = 265.12.
\end{align}

We proceed in the same away for the quartic EFT. Here we use Eq.~(68) (with
$\epsilon_{1} = 1$ and $\epsilon_{2} = 0$) and Eq.~(70) of
Ref.~\cite{Cano:2021myl},
%
In this case we found that both modes (``-'' and ``+'' in the notation of Ref.~\cite{Cano:2020cao}) make the
fundamental QNM damp fast and we chose the ``-'' mode which decreases less the damping time.
%
We then find
%
\begin{align}
    p_{\rm qEFT} = 6, \quad \delta \omega_{\rm qEFT}^{(0)} = -0.2114, \quad \delta \tau_{\rm qEFT}^{(0)} = -0.6070,
    \nonumber \\
    \delta \omega_{\rm qEFT}^{(1)} = -1.5263, \quad \delta \tau_{\rm qEFT}^{(1)} = 171.35.
\end{align}
